CMP_monocle

### 2021-12-14 monocle/IndividualPops_monocle.Rmd
added gene expression and trajectory overlay plots to script

>>>>

## Plot by gene expression
```{r}
my_plot <- plot_cells(cds, reduction_method = "UMAP", 
            genes = c("Elane", "Fli1", "Gata1", "Gata2", "Klf1", "Meis1", "Zfpm1", "Dntt", "Cd150"), trajectory_graph_color = "red",
            label_groups_by_cluster = FALSE, label_leaves = FALSE, label_branch_points = TRUE,  
            cell_size = 1, group_label_size = 8, graph_label_size = 5, trajectory_graph_segment_size = 1)
plot(my_plot)

png(filename = paste0(projectName, "-umap_YFG_psdtime.png"), height = 1600, width = 2000, bg = "transparent")
plot(my_plot)
dev.off()
```
